Continous time Markov chain models; \\ extension, simulation and visualisation

### 2015-01-16 Response.tex

\begin{itemize}

% 1
\item {
{\it
\textbf{
The thesis starts with a very nice introduction, which I think is very insightful for the reader who is not familiar with phylogenetic and/or Bayesian inference. 
In spite of this, I believe that the readability of the later chapters would be further improved if the introduction:
}% END: textbf
}% END: it
}% END: item

\begin{itemize}

% 1a
\item {
{\it
\textbf{
Briefly described the evolutionary models, such as GY94, that are later used.
}% END: textbf
}% END: it
}% END: item
\\
Done, there is now a \emph{Markov models of codon evolution} section in the introductory chapter.

% 1b
\item {
{\it
\textbf{
Briefly described how to accommodate time-stamped sequences, which is now considered in the analyses in Chapter 2, but not really discussed.
}% END: textbf
}% END: it
}% END: item
\\
AAA

% 1c
\item {
{\it
\textbf{
Give a bit more detail on phylogeography, e.g. how do the models look like and what is the connection between phylogeography and epoch models (some connection is described in Chapter 2, but remains a bit vague).
}% END: textbf
}% END: it
}% END: item
\\
AAA

### 2015-01-19 frontback/acknowledgments.tex
cleanup
typo, B-W moore figure
simulations, acknowledgements

TODO

@@

The research leading to these results has received funding from the European Research Council under the European Community's Seventh Framework Programme (FP7/2007-2013) under Grant Agreement no. 278433-PREDEMICS and ERC Grant agreement no. 260864, the Welcome Trust (grant no. 092807) and the National Institutes of Health (R01 GM086887 and R01 HG006139) and the National Science Foundation (IIS 1251151 and DMS 1264153).
The National Evolutionary Synthesis Center (NESCent) catalyzed this collaboration through a working group (NSF EF-0423641). LMC would like to thank the Program for Scientific Computing staff for operational support.

>>>>

\medskip{}

\begin{flushright}
\emph{Mojej Babci.}
\par\end{flushright}

\medskip{}

First and foremost my special appreciation and thanks go to my promotor Prof. Philippe Lemey, for his guidance, without which this work would not be possible, and for being a constant source of inspiration. 
Despite being a world-class researcher Prof. Lemey remains the kindest, most humble and modest person that I have ever met, not only the scientist I would like to become but also the kind of person I would like to
be.

I am grateful for the insightful suggestions and all the help I received from my co-promotor and fellow lab member Guy Baele.

I am also indebted to my collaborators, Prof. Marc Suchard for hosting me numerous times in Los Angeles, for his statistical and computational expertise which he generously shares and which has taugh me so much, and to Prof. Andrew Rambaut, from whom I have learned a lot about developing scientific software which is not only usable but also a pleasure to use.

I would like to thank the jury members Prof. David Posada, Prof. Stijn Vansteelandt, Prof. Stein Aerts, Prof. Geert Molenberghs and Prof. Peter Hoet for their comments and suggestions on this thesis, as well as for serving as my committee members.

\paragraph{} 
To all my past and present friends from the Evolutionary and Computational Virology laboratory, Bram Vrancken, Guy Baele, Nidia Trovao, Nuno Faria for all the good work, good times, good beers and jenevers we had together.

To my friends from Belgium, with whom I have spent wonderful times climbing in the Ardennes. 
Freyr is the next best thing since sliced bread.

My friends from Poland, who I don't see as often as I would like to, but when we meet it is always something to remember. 
Wojtkowi - za pogod\k{e} ducha. 
Adamowi - \.{z}eby\'{s} zawsze wszystkich przechytrzy\l{}.
Kamilowi - uwa\.{z}aj na p\l{}oty. 
Ma\'{c}kowi - za wsp\'{o}lne wspinanie.
Marcinowi - widzimy si\k{e} za rzadko, wi\k{e}c pijemy za szybko.

\emph{`In the moment when I'm on the summit there is no explosion of happiness - happiness is something experienced when everything remains in front of you, when you know that to reach the peak you have only a few hundred, a few dozen meters, when it is right in front of you. This is the time of happiness.'} 
---Jerzy Kukuczka

Justyna - szcz\k{e}\'{s}cie to my i nasze \.{z}ycie, szcz\k{e}\'{s}cie jest tu i teraz.

Finally this thesis is dedicated to my family, my grandmother, my parents, my godmother, my aunt and my brother. 
Mamo, Tato, Babciu, Kasper, Ciociu, Igo - ciesze si\k{e} \.{z}e mogli\'{s}cie tu by\'{c} \.{z}eby
dzieli\'{c} t\k{e} chwil\k{e} ze mn\k{a}.

\begin{flushright}
Filip Zbigniew Bielejec \\
\textit{KU Leuven, Belgium} \\
March 2015
\par\end{flushright}

@@

The research leading to these results has received funding from the European Research Council under the European Community's Seventh Framework Programme (FP7/2007-2013) under Grant Agreement no. 278433-PREDEMICS and ERC Grant agreement no. 260864, the Welcome Trust (grant no. 092807) and the National Institutes of Health (R01 GM086887 and R01 HG006139) and the National Science Foundation (IIS 1251151 and DMS 1264153).
The National Evolutionary Synthesis Center (NESCent) catalyzed this collaboration through a working group (NSF EF-0423641).
